---
title: "Vegvisir CrossFit Survey Results"
output:
  rmdformats::readthedown:
    # code_folding: show
    self_contained: true
    thumbnails: false
    lightbox: false
css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## put these first
library(lessR)
library(wordcloud)
library(tm)
## 
library(tidyverse)
library(janitor)
library(wordcloud2)
library(reactable)
library(gt)
library(ggeasy)
library(ggpubr)
library(scales)

hc1<-"#b6e0fa"
hc2<-"#132960"
hc3<-"#036da7"
hc4<-"#e3b23c"
hc5 <-"#c884a6"
hc6<-"#95e06c"
hc7<-"#f0a6ca"

my_pallete<-c(hc1,hc2,hc3,hc4,hc5,hc6,hc7)

theme_set(theme_classic() +
            easy_remove_legend() +
            easy_text_size(15))

# scale_colour_continuous <- scale_colour_viridis_c
# scale_colour_discrete <- scale_colour_viridis_d
# scale_colour_binned <- scale_colour_viridis_b
```


```{r}
raw_data <- read_csv("survey_data.csv") %>%
  clean_names()

clean_data <- raw_data %>%
  rename(years = how_long_have_you_been_doing_cross_fit,
         motivation = what_motivated_you_to_join_our_cross_fit_gym,
         nerves = did_you_have_any_hesitations_nerves_when_joining_vegvisir_cross_fit_or_attending_your_first_class, 
         nclass = how_many_classes_do_you_usually_attend_a_week,
         workout_other = do_you_workout_outside_of_cross_fit_if_so_what_do_you_typically_do_e_g_running_swimming_cycling_etc_and_how_many_times_per_week,
         gyms_other = do_you_belong_to_any_other_gyms_or_health_facilities_clubs_outside_of_vegvisir_if_yes_please_describe,
         fav_modality = what_is_your_favorite_modality,
         movement_scared = what_movement_scares_your_the_most,
         lift_improve = what_lift_would_you_like_to_improve_the_most,
         gymnastics_improve = which_gymnastic_movement_would_you_like_to_improve_the_most,
         movement_fav = what_is_your_favorite_cross_fit_movement_including_lifts_and_gymnastics,
         goal_review = did_you_find_your_last_goal_review_added_value_to_your_training,
         vegvisir_love = what_do_you_love_most_about_being_a_vegvisir_athlete,
         suggestions = do_you_have_any_suggestions_or_recommendations_for_vegvisir_cross_fit) %>%
  select(-timestamp)
```

# How long have you been doing crossfit?
```{r}

clean_data$years <- factor(clean_data$years, levels = c("5+ years", "3-5 years", "1-3 years", "6-12 months", "0-6 months"))


PieChart(years, data = clean_data,
         hole = 0.0,
         color = "black",
         lwd = 1.5,
         lty = 1,
         main = NULL,
         values_size = 1,
         cex = 1.5,
         quiet = TRUE, 
         fill = my_pallete)

# years_pie <- clean_data %>% 
#   select(years) %>%
#   group_by(years) %>%
#   count(years) %>%
#   ungroup() %>%
#   mutate(pct = n / sum(n))
# 
# ggplot(years_pie, aes(x = "", y = pct, fill = years)) +
#   geom_bar(stat = "identity", color = "white") +
#   geom_text(aes(x = 1.6, label = scales::percent(pct, accuracy = .1)), position = position_stack(vjust = .5)) +
#   coord_polar("y") +
#   theme_void()

```

# What motivated you to join our CrossFit gym?

```{r include=FALSE}
motivation_data <- clean_data %>%
  select(motivation)
motivation_data <- mutate_all(motivation_data, .funs=tolower)

motivation_data <- mutate(motivation_data, 
                          Health = str_detect(motivation_data$motivation, regex("health|better care|stress|healthier|fitness|cancer survivor|shape|weight")), 
                          "Getting Stronger" = str_detect(motivation_data$motivation, regex("fitter|olympics")),
                          Location = str_detect(motivation_data$motivation, regex("location|close|closest|proximity|luck")),
                          Vegvisir = str_detect(motivation_data$motivation, regex("programming|coaches|coaching|quality|nice|clean|staff|community|culture|atmosphere")),
                          Covid = str_detect(motivation_data$motivation, regex("covid")),
                          Enjoyable = str_detect(motivation_data$motivation, regex("fun|interested"))) 

motivation_themes <- motivation_data %>%
  summarise(across(Health:Enjoyable, ~ sum(., na.rm = TRUE))) %>%
  pivot_longer(Health:Enjoyable, names_to = "theme")

ggplot(motivation_themes, aes(x = reorder(theme, value), y = value, fill=theme)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = "", y = "") + 
  scale_fill_manual(values = my_pallete)
  

```


```{r}
corpus <- Corpus(VectorSource(clean_data$motivation))

# corpus[[1]][[1]]
# corpus[[2]][[1]]

corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers) 
corpus <- tm_map(corpus, removeWords, stopwords("english")) # remove english common stopwords "a", "the", etc.
corpus <- tm_map(corpus, removePunctuation) 
corpus <- tm_map(corpus, stripWhitespace) 
corpus <- tm_map(corpus, removeWords, c("went", "something", "get", "better", "wanted", "take", "apartment", "crossfit", "looking", "great", "houston", "just", "really", "needed", "gym"))
#corpus <- tm_map(corpus, stemDocument)

# create TDM
tdm <- TermDocumentMatrix(corpus)
m <- as.matrix(tdm)
v <- sort(rowSums(m), decreasing=TRUE)
d <- data.frame(word = names(v), freq=v) %>%
  filter(freq > 1)

set.seed(2)
wordcloud2(d, size = .5, shuffle = FALSE, color='random-light', backgroundColor="black")

```


```{r}
motivation <- clean_data %>%
  select(motivation) %>%
  rename("Motiavtion" = motivation)

reactable(motivation, striped = TRUE)
```


# Did you have any hesitations/nerves when joining Vegvisir CrossFit or attending your first class?

```{r include=TRUE}
nerves_data <- clean_data %>%
  select(nerves) 
                              
nerves_data <- mutate_all(nerves_data, .funs=tolower)

patterns_yes <- regex("yes|yeah|scared|scary|fear|silly|didnt feel confident")
patterns_no <- regex("no$|nope|not really|not much|no/s|no i had done crossfit previously")

nerves_pie <- nerves_data %>%
  mutate(across(everything(), ~gsub("[[:punct:]]", "", .x)),
         nerves_yes_no = case_when(str_detect(nerves, patterns_yes) ~ "Yes",
                            str_detect(nerves, patterns_no) ~ "No",
                            TRUE ~ "N/A")) %>%
  filter(nerves_yes_no != "N/A")

# nerves_data %>%
#   mutate(across(everything(), ~gsub("[[:punct:]]", "", .x)),
#          nerves_yes_no = case_when(str_detect(nerves, patterns_yes) ~ "Yes",
#                             str_detect(nerves, patterns_no) ~ "No",
#                             TRUE ~ "N/A")) %>%
#   filter(nerves_yes_no != "N/A") %>%
#   group_by(nerves_yes_no) %>%
#   count()

PieChart(nerves_yes_no, data = nerves_pie,
         hole = 0.0,
         color = "black",
         lwd = 1.5,
         lty = 1,
         main = NULL,
         values_size = 1,
         cex = 1.5,
         quiet = TRUE, 
         fill = my_pallete)

# nerves_pie <- nerves_data %>%
#   mutate(yes = str_detect(nerves,patterns_yes),
#          no = str_detect(nerves,patterns_no))  %>%
#   summarise(across(yes:no, sum)) %>%
#   pivot_longer(yes:no, names_to = "nerves") %>%
#   mutate(pct = value / sum(value))
# 
# ggplot(nerves_pie, aes(x = "", y = pct, fill = nerves)) +
#   geom_bar(stat = "identity", color = "white") +
#   geom_text(aes(x = 1.6, label = scales::percent(pct, accuracy = .1)), position = position_stack(vjust = .5)) +
#   coord_polar("y") +
#   theme_void() +
#   easy_remove_legend_title()
# 
# nerves_pie2 <- nerves_data %>%
#   mutate(yes = str_detect(nerves,patterns_yes),
#          no = str_detect(nerves,patterns_no))



```

# How many classes do you usually attend a week?
```{r}
clean_data$nclass <- factor(clean_data$nclass, levels = c(5,4,3,2),
                            labels = c("5 Classes", "4 Classes", "3 Classes", "2 Classes"))

PieChart(nclass, data = clean_data,
         hole = 0.0,
         color = "black",
         lwd = 1.5,
         lty = 1,
         main = NULL,
         values_size = 1,
         cex = 1.5,
         quiet = TRUE, 
         fill = my_pallete)

# nclass_pie <- clean_data %>% 
#   select(nclass) %>%
#   group_by(nclass) %>%
#   count(nclass) %>%
#   ungroup() %>%
#   mutate(pct = n / sum(n))
# 
# ggplot(nclass_pie, aes(x = "", y = pct, fill = nclass)) +
#   geom_bar(stat = "identity", color = "white") +
#   # geom_text(aes(x = 1.6, label = nclass), position = position_stack(vjust = .5)) +
#   # geom_text(aes(label = scales::percent(pct, accuracy = .1)),
#   #           position = position_stack(vjust = 0.5)) +
#   geom_text(aes(x = 1.6, label = scales::percent(pct, accuracy = .1)), position = position_stack(vjust = .5)) +
#   coord_polar("y") +
#   theme_void() +
#   easy_remove_legend_title()

```

# What type of exercise do you do outside of crossfit?

```{r}
corpus_workout <- Corpus(VectorSource(clean_data$workout_other))

corpus_workout <- tm_map(corpus_workout, content_transformer(tolower))
corpus_workout <- tm_map(corpus_workout, removeNumbers) 
corpus_workout <- tm_map(corpus_workout, removeWords, stopwords("english")) # remove english common stopwords "a", "the", etc.
corpus_workout <- tm_map(corpus_workout, removePunctuation) 
corpus_workout <- tm_map(corpus_workout, stripWhitespace) 
corpus_workout <- tm_map(corpus_workout, removeWords, c("week", "times", "yes", "sometimes", "per", "maybe", "day", "every", "xweek"))
#corpus <- tm_map(corpus, stemDocument)

# create TDM
tdm_workout <- TermDocumentMatrix(corpus_workout)
m_workout <- as.matrix(tdm_workout)
v_workout <- sort(rowSums(m_workout), decreasing=TRUE)
d_workout <- data.frame(word = names(v_workout), freq=v_workout) %>%
  filter(freq > 1)

d_workout <- d_workout %>%
  as_tibble() %>%
  mutate(word = ifelse(word == "run", "running", word),
         word = factor(word)) %>%
  group_by(word) %>%
  dplyr::summarise(freq = sum(freq))

# set.seed(2)
# wordcloud2(d_workout, color = "random-dark", backgroundColor = "white", size = .3, shuffle = FALSE)

ggplot(d_workout, aes(x = reorder(word, freq), freq, fill = word)) +
  geom_col() +
  coord_flip() +
  labs(x = "", y = "") + 
  scale_fill_manual(values = my_pallete)

```


# Do you belong to any other gyms or health facilities/clubs outside of Vegvisir?

```{r}

gym_data <- clean_data %>%
  select(gyms_other) 
                              
gym_data <- mutate_all(gym_data, .funs=tolower)

gym_pie <- gym_data %>%
  mutate(across(everything(), ~gsub("[[:punct:]]", "", .x)),
         outside_gym = ifelse(gyms_other %in% c("no", "na", "nope"), FALSE, TRUE))

gym_pie$outside_gym <- factor(gym_pie$outside_gym, labels = c("No", "Yes"))

PieChart(outside_gym, data = gym_pie,
         hole = 0.0,
         color = "black",
         lwd = 1.5,
         lty = 1,
         main = NULL,
         values_size = 1,
         cex = 1.5,
         quiet = TRUE, 
         fill = my_pallete)
                        
```


# What is your favorite modality?

```{r}
# unique(clean_data$fav_modality)

modality_data <- clean_data %>%
  select(fav_modality) %>%
  mutate(modality = case_when(fav_modality == "Cardio Monster (Bike, Jump Rope, Running, Rowing, etc...)" ~ "Cardio Monster",
                              fav_modality == "Gymnastics (Pull-ups, Muscle-Ups, Pistols, Box Jumps, etc...)" ~ "Gymnastics",
                              fav_modality == "Olympic Lifting (Snatch, Clean, and Jerk)" ~ "Olympic Lifting",
                              fav_modality == "Power Lifting (Back Squat, Deadlift, Shoulder Press, and Bench Press)" ~ "Power Lifting",
                              TRUE ~ 'Other')) %>%
  group_by(modality) %>%
  count() 


modality_data$modality <- factor(modality_data$modality)
#modality_data$n <- factor(modality_data$n)

ggplot(modality_data, aes(x = reorder(modality, n), y = n, fill=modality)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = "", y = "") +
  scale_y_continuous(breaks= pretty_breaks()) + 
  scale_fill_manual(values = my_pallete)


```

# What movement scares your the most?

```{r}
scary_data <- clean_data %>%
  select(movement_scared) %>%
  mutate(movement = case_when(movement_scared == "Inversions (Handstands, Handstand Push-Ups, Box HSPU)" ~ "Inversions",
                            TRUE ~ movement_scared)) %>%
  group_by(movement) %>%
  count() 


scary_data$movement <- factor(scary_data$movement)
#modality_data$n <- factor(modality_data$n)

ggplot(scary_data, aes(x = reorder(movement, n), y = n, fill=movement)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = "", y = "") +
  scale_y_continuous(breaks= pretty_breaks()) + 
  scale_fill_manual(values = my_pallete)

#################
clean_data$years <- factor(clean_data$years)

scary_data_yrs <- clean_data %>%
  select(movement_scared, years) %>%
  mutate(movement = case_when(movement_scared == "Inversions (Handstands, Handstand Push-Ups, Box HSPU)" ~ "Inversions",
                            TRUE ~ movement_scared)) %>%
  group_by(movement, years) %>%
  count() 

scary_data_yrs$years <- factor(scary_data_yrs$years, levels = c("0-6 months", "6-12 months", "1-3 years", "3-5 years", "5+ years"))

ggplot(scary_data_yrs, aes(x = reorder(movement, n), y = n, fill=movement)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  facet_wrap(~years) +
  labs(x = "", y = "") +
  scale_y_continuous(breaks= pretty_breaks()) + 
  scale_fill_manual(values = my_pallete)

```

# What lift would you like to improve the most?

```{r}
improve_data <- clean_data %>%
  select(lift_improve) %>%
  group_by(lift_improve) %>%
  count() %>%
  na.omit() %>%
  filter(lift_improve != "I’ve always enjoyed the programming and rotation of all of the above.") %>%
  filter(lift_improve != "MUs, handstand walk, HSPU")


improve_data$lift_improve <- factor(improve_data$lift_improve)
#modality_data$n <- factor(modality_data$n)

ggplot(improve_data, aes(x = reorder(lift_improve, n), y = n, fill=lift_improve)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = "", y = "") +
  scale_y_continuous(breaks= pretty_breaks()) + 
  scale_fill_manual(values = my_pallete)

############

improve_data_yrs <- clean_data %>%
  select(lift_improve, years) %>%
  group_by(lift_improve, years) %>%
  count() %>%
  na.omit() %>%
  filter(lift_improve != "I’ve always enjoyed the programming and rotation of all of the above.") %>%
  filter(lift_improve != "MUs, handstand walk, HSPU")

improve_data_yrs$years <- factor(improve_data_yrs$years, levels = c("0-6 months", "6-12 months", "1-3 years", "3-5 years", "5+ years"))

ggplot(improve_data_yrs, aes(x = reorder(lift_improve, n), y = n, fill=lift_improve)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  facet_wrap(~years) +
  labs(x = "", y = "") + 
  scale_fill_manual(values = my_pallete)
```

# Which gymnastic movement would you like to improve the most?

```{r}
gymnastic_improve_data <- clean_data %>%
  select(gymnastics_improve) %>%
   mutate(gymnastics_improve = case_when(gymnastics_improve == "Double Unders (Yeah we know these are cardio)" ~ "Double Unders",
                               TRUE ~ gymnastics_improve)) %>%
  group_by(gymnastics_improve) %>%
  count()

gymnastic_improve_data$gymnastics_improve <- factor(gymnastic_improve_data$gymnastics_improve)
#modality_data$n <- factor(modality_data$n)

ggplot(gymnastic_improve_data, aes(x = reorder(gymnastics_improve, n), y = n, fill=gymnastics_improve)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = "", y = "") +
  scale_y_continuous(breaks= pretty_breaks()) + 
  scale_fill_manual(values = my_pallete)
```

# What is your favorite CrossFit movement (including lifts and gymnastics)?

```{r}
favorite_data <- clean_data %>%
  select(movement_fav) %>%
  rename( "Favorite Movement" = movement_fav)

reactable(favorite_data, striped = TRUE)
```

# What do you love most about being a Vegvisir athlete?

```{r fig.width=8, fig.height=5}
corpus <- Corpus(VectorSource(clean_data$vegvisir_love))

# corpus[[1]][[1]]
# corpus[[2]][[1]]

corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers) 
corpus <- tm_map(corpus, removeWords, stopwords("english")) # remove english common stopwords "a", "the", etc.
corpus <- tm_map(corpus, removePunctuation) 
corpus <- tm_map(corpus, stripWhitespace) 
corpus <- tm_map(corpus, removeWords, c("part", "day", "just", "sense", "feel", "always", "whole", "good"))
#corpus <- tm_map(corpus, stemDocument)

# create TDM
tdm <- TermDocumentMatrix(corpus)
m <- as.matrix(tdm)
v <- sort(rowSums(m), decreasing=TRUE)
d <- data.frame(word = names(v), freq=v) %>%
  filter(freq > 1)

set.seed(2)
wordcloud2(d, size = .7, shuffle = FALSE, color='random-light', backgroundColor="black")
```

